### 2022-08-02 paper/akweury/document.tex
update an2

%% mean metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & & 9.82 \\ 
		\hline
		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & & 7.32\\ 
		\hline
		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & & 7.35 \\
		\hline
		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & & 9.15 \\
		\hline
		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & & 12.13\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & & 7.62 \\ 
		\hline
		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & & 4.01 \\ 
		\hline
		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & & 5.06 \\
		\hline
		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & & 5.81\\
		\hline
		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & & 6.76\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l |l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & & 0.31\\ 
		\hline
		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & & 0.59 \\ 
		\hline
		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & & 0.50\\
		\hline
		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & & 0.45\\
		\hline
		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & & 0.41\\
	\end{tabular}
	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & & 0.69\\ 
		\hline
		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & & 0.83 \\ 
		\hline
		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & & 0.82\\
		\hline
		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & & 0.75\\
		\hline
		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & & 0.66\\
	\end{tabular}
	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & & 0.92\\ 
		\hline
		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & & 0.94\\ 
		\hline
		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & & 0.95\\
		\hline
		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & & 0.91\\
		\hline
		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & & 0.84\\
	\end{tabular}
	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & & 0.97 \\ 
		\hline
		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & & 0.96 \\ 
		\hline
		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & & 0.98 \\
		\hline
		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & & 0.95 \\
		\hline
		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & & 0.90\\
	\end{tabular}
	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
	\label{tab:eval-30d}
\end{table}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
	\caption{SVD}
\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
		\caption{Trip-Net}
	\end{subfigure}

		\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_point_cloud_noise.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_img.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}

	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ dataset. The first row is surface normal, the second row is the corresponding errors. }
	\label{fig:high_resolution_eval}
\end{figure}

\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.20 & 8.90 & 8.30\\ 
		\hline
		Median					& 4.87 & 5.82 & 5.14 \\ 
		\hline
		$ 5^\circ $ 			& 0.51 & 0.43 & 0.49 \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.80 \\
		\hline
		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
		\hline
		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes.}	
	\label{tab:high_resolution_eval}
\end{table}

>>>>

%% mean metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 35.66 & 11.09 & 13.58 & 15.55 & 11.22 & 10.36 & 9.77 & 9.80 \\ 
		\hline
		Bus 			& 20 & 31.93 & 7.79 & 8.95 & 11.93 & 7.49 & 7.85 & 7.30 & 7.62\\ 
		\hline
		Dragon 			& 20 & 39.57 & 10.60 & 15.29 & 16.03 & 10.47 & 10.23 & 8.16 & 7.79 \\
		\hline
		Garfield 		& 20 & 39.69 & 10.20 & 12.50 & 14.46 & 9.94 & 10.36 & 9.71 & 9.39 \\
		\hline
		Washington 		& 20 & 42.83 & 13.43 & 17.59 & 18.71 & 13.32 & 13.40 & 12.62 & 12.60\\
	\end{tabular}
	\caption{Average Angle Error of the evaluation dataset.}	
	\label{tab:eval-mean}
\end{table}

%% median metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 34.06 & 8.86 & 10.82 & 13.25 & 8.95 & 8.02 & 7.54 & 7.50 \\ 
		\hline
		Bus 			& 20 & 34.14 & 4.44 & 5.02 & 8.69 & 4.11 & 4.58 & 3.65 & 4.47 \\ 
		\hline
		Dragon 			& 20 & 36.43 & 7.62 & 11.10 & 13.26 & 7.60 & 7.12 & 5.87 & 5.52 \\
		\hline
		Garfield 		& 20 & 37.60 & 6.40 & 8.90 &11.31 & 6.30 & 6.72 & 6.21 & 6.04 \\
		\hline
		Washington 		& 20 & 36.89 & 7.64 & 11.38 & 13.64& 7.49 & 7.60 & 7.03 & 7.25\\
	\end{tabular}
	\caption{Median Angle Error of the evaluation dataset.}	
	\label{tab:eval-median}
\end{table}

%% 5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l |l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.01 & 0.25 & 0.18 & 0.11 & 0.24 & 0.31 & 0.33 & 0.32\\ 
		\hline
		Bus 			& 20 & 0.00 & 0.56 & 0.50 & 0.23 & 0.59 & 0.54 & 0.63 & 0.55 \\ 
		\hline
		Dragon 			& 20 & 0.00 & 0.31 & 0.17 & 0.10 & 0.31 & 0.34 & 0.43 & 0.46\\
		\hline
		Garfield 		& 20 & 0.00 & 0.41 & 0.27 & 0.14 & 0.42 & 0.39 & 0.42 & 0.43\\
		\hline
		Washington 		& 20 & 0.00 & 0.38 & 0.26 & 0.10 & 0.36 & 0.36 & 0.40 & 0.37\\
	\end{tabular}
	\caption{Percent of error less than 5 degree of the evaluation dataset.}	
	\label{tab:eval-5d}
\end{table}

%% 11.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.03 & 0.62 & 0.52 & 0.41 &  0.62 & 0.66 & 0.69 & 0.69\\ 
		\hline
		Bus 			& 20 & 0.05 & 0.81 & 0.78 & 0.65 & 0.83 & 0.82 & 0.83 & 0.83 \\ 
		\hline
		Dragon 			& 20 & 0.02 & 0.69 & 0.51 & 0.40 & 0.70 & 0.71 & 0.79 & 0.81\\
		\hline
		Garfield 		& 20 & 0.03 & 0.72 & 0.62 & 0.51 &0.73 & 0.71  & 0.74 & 0.75\\
		\hline
		Washington 		& 20 & 0.02 & 0.62 & 0.50 & 0.40 & 0.63 & 0.62 & 0.64 & 0.65\\
	\end{tabular}
	\caption{Percent of error less than 11.5 degree of the evaluation dataset.}	
	\label{tab:eval-11d}
\end{table}

%% 22.5 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.18 & 0.90 & 0.84 & 0.79 & 0.90 & 0.91 & 0.92 & 0.92\\ 
		\hline
		Bus 			& 20 & 0.26 & 0.93 & 0.91 & 0.89 & 0.93 & 0.93 & 0.93 & 0.94\\ 
		\hline
		Dragon 			& 20 & 0.14 & 0.90 & 0.79 & 0.80 & 0.90 & 0.90 & 0.94 & 0.95\\
		\hline
		Garfield 		& 20 & 0.13 & 0.89 & 0.86 & 0.84 & 0.90 & 0.89 & 0.91 & 0.91\\
		\hline
		Washington 		& 20 & 0.14 & 0.81 & 0.72 & 0.72 & 0.81 & 0.81 & 0.83 & 0.83\\
	\end{tabular}
	\caption{Percent of error less than 22.5 degree of the evaluation dataset.}	
	\label{tab:eval-22d}
\end{table}

%% 30 degree metric
\begin{table}[H]
	\centering
	\begin{tabular}{l l | l | l l l | l l l l }
		\tabhead{Object} & $ \# $ & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{NOC} & \tabhead{CNN} & \tabhead{F1}& \tabhead{F2}& \tabhead{F3}& \tabhead{F4}\\
		Baoshanlu  		& 20 & 0.37 & 0.96 & 0.93 & 0.90 & 0.96 & 0.96 & 0.97 & 0.97 \\ 
		\hline
		Bus 			& 20 & 0.43 & 0.96 & 0.94 & 0.93 & 0.96 & 0.96 & 0.96 & 0.96 \\ 
		\hline
		Dragon 			& 20 & 0.30 & 0.95 & 0.88 & 0.90 & 0.95 & 0.95 & 0.97 & 0.98 \\
		\hline
		Garfield 		& 20 & 0.27 & 0.94 & 0.92 & 0.91 & 0.94 & 0.94 & 0.94 & 0.95 \\
		\hline
		Washington 		& 20 & 0.28 & 0.88 & 0.81 & 0.82 & 0.88 & 0.88 & 0.89 & 0.89\\
	\end{tabular}
	\caption{Percent of error less than 30 degree of the evaluation dataset.}	
	\label{tab:eval-30d}
\end{table}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_SVD.png}
\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_NNNN-512.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_normal_An2-real-resume.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_real/00008.image0.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_SVD.png}
	\caption{SVD}
	\end{subfigure}	
	\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_NNNN-512.png}
	\caption{GCNN}
	\end{subfigure}
\begin{subfigure}[b]{0.24\linewidth}
	\includegraphics[width=\linewidth]{./Figures/comparison_real/fancy_eval_0_error_An2-real-resume.png}
	\caption{Trip-Net}
\end{subfigure}	
	\caption{Comparison between different SVD, GCNN and Trip-Net model on $ 512\times 512 $ real dataset. The first row is surface normal, the second row is the corresponding errors. }
	\label{fig:high_resolution_eval}
\end{figure}

\begin{table}[H]
	\centering
	\begin{tabular}{l l l l }
		\tabhead{Metrics} & \tabhead{SVD} & \tabhead{GCNN} & \tabhead{Trip-Net} \\
		Mean  					& 8.20 & 8.90 & 8.30\\ 
		\hline
		Median					& 4.87 & 5.82 & 5.14 \\ 
		\hline
		$ 5^\circ $ 			& 0.51 & 0.43 & 0.49 \\
		\hline
		$ 11.5^\circ $ 			& 0.79 & 0.78 & 0.80 \\
		\hline
		$ 22.5^\circ $ 			& 0.93 & 0.93 & 0.93 \\
		\hline
		$ 30^\circ $ 			& 0.96 & 0.96 & 0.96\\
	\end{tabular}
	\caption{Evaluation of SVD, GCNN and Trip-Net models on 6 different metrics based on 100 test scenes in real dataset.}	
	\label{tab:high_resolution_eval}
\end{table}
